Paper notes

### 2019-08-05 paper_notes.Rmd
Add files via upload

#old
# f <- function(p,M,x,n){
#  if (x  <= (n*p)){U <- (x/(n*p))}
#  else {U <- M + ((1-(x/n))*(1-M))/(1-p)}
 # else {U <- (2-M) + (((M-1)*x)/(n*p))} M + ((1-(x/n))*(1-M))/(1-p)}
#  round(U,digits = 3)
# }

#f_dist <- function(o,ot,M,i,S){
#  if (abs(o-ot) < i) {
#    U <- (abs(o-ot)/i) * S
#    }else if (abs(o-ot) > i){
#      U <- M + ((1-abs(o-ot))*(1-M))/(1-i)
#    }else{
#        U <- 1}
#  round(U,digits = 3)
#  }

#f_val <- function(o,ot,M,i,S){
# if (round(abs(o-ot), digits=2) >= i) {
#    U <- 1
#  }else {
#      U <- # (1 - (1-(abs(o-ot))/i) * S)
#         1 -  (M + ((1-(1-abs(o-ot)))/(1-M))/(1-(1-i)))
#       1 - (M + ((1-(1-abs(o-ot)))*(1-M))/(1-(1-i)))
#    }
#  round(U,digits = 3)
#  }

#f_val_repr <- function(sim,M,i,S){
#  if (sim <= i) {
#    U <- sim/i * S
#     }else if (sim > i){
# U <- M + ((1-sim)*(1-M))/(1-i)
#    }else{
#         U <- 1}
#   round(U,digits = 3)
#   }

@@

# library(namelibrary) for the R library

# http://rmarkdown.rstudio.com
# echo = TRUE <- makes all next cmds appear

@@

@@

f_val <- function(o,ot,M,i,S){
  if (round(abs(o-ot), digits=2) <= i) {
    U <- 1
    }else{
      U <- (M + ((1-(round(abs(o-ot), digits=2)))*(1-M))/(1-i)) * S
    }
  round(U,digits = 2)
  }

i <- 0.2
S  <- 1
M <- 0

@@

for (o in seq (0.0,1.0, by = 0.1)){

fv0d2 <- f_val(o,0,M,i,S)
fv1d2 <- f_val(o,0.1,M,i,S)
fv2d2 <- f_val(o,0.2,M,i,S)
fv3d2 <- f_val(o,0.3,M,i,S)
fv4d2 <- f_val(o,0.4,M,i,S)
fv5d2 <- f_val(o,0.5,M,i,S)
fv6d2 <- f_val(o,0.6,M,i,S)
fv7d2 <- f_val(o,0.7,M,i,S)
fv8d2 <- f_val(o,0.8,M,i,S)
fv9d2 <- f_val(o,0.9,M,i,S)
fv10d2 <- f_val(o,1.0,M,i,S)

value_mean_neighborhood <- seq(0.0, 1.0, by = 0.1)
Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
name <- paste0("Ethnic weight i = ", o,";distance desired i = ",i,"; M = ",M,"; S = ",S)

@@

report <- paste0("M = ",M," ??? S = ",S," ??? Ethnic weight i = ",o, " ??? desired distance i = ",i," ??? Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), " ??? Utility ij = ", Utility_V)

print(report)

@@

```{ethnic utility, moore neighborhood}

f_eth <- function(p,M,x,n,S){
  if (x  < (n*p)){
    U <- (x / (n*p)) * S
    }else if (x > (n*p)){
      U <- M + ((1-(x/n))*(1-M))/(1-p)
    }else{
        U <- 1}
  round(U,digits = 2)
}

p = 0.5
M = 1
S = 1

f0m <- f_eth(p,M,0,8,S)
f1m <- f_eth(p,M,1,8,S)
f2m <- f_eth(p,M,2,8,S)
f3m <- f_eth(p,M,3,8,S)
f4m <- f_eth(p,M,4,8,S)
f5m <- f_eth(p,M,5,8,S)
f6m <- f_eth(p,M,6,8,S)
f7m <- f_eth(p,M,7,8,S)
f8m <- f_eth(p,M,8,8,S)

ethnic_concentration_neighborhood <- seq(0.0, 0.8, length.out = 9)
Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)

# print(utilitym)
print(c("Ethnic Utility",Utility_E)) 
plot(ethnic_concentration_neighborhood,Utility_E,title("Ethnic Utility"))

@@

prob <- function(l,s,t,d,p,q){1 / (1 + exp(-l*(s-t)) + exp(-d*(p-q)))}

prob1 <- prob(100,300,100,1,100,100)
plot(prob1)
```

@@

```{r vn, echo=FALSE, include=FALSE, fig.cap="utility in Von Neumann 4 patches; desired fraction 50%, M=0.6, Z=1"}

f0vn <- f(0.5,0.6,0,4)
f1vn <- f(0.5,0.6,1,4)
f2vn <- f(0.5,0.6,2,4)
f3vn <- f(0.5,0.6,3,4)
f4vn <- f(0.5,0.6,4,4)

utilityvn <- c(f0vn,f1vn,f2vn,f3vn,f4vn)
concentrationvn <- c(0:4)

#print(utilityvn)
plot(concentrationvn,utilityvn)

```{r R2,include=FALSE, echo=FALSE, fig.cap="utility in R2 12 patches; desired fraction 50%, M=0.6, Z=1"}

f0r2 <- f(0.5,0.6,0,12)
f1r2 <- f(0.5,0.6,1,12)
f2r2 <- f(0.5,0.6,2,12)
f3r2 <- f(0.5,0.6,3,12)
f4r2 <- f(0.5,0.6,4,12)
f5r2 <- f(0.5,0.6,5,12)
f6r2 <- f(0.5,0.6,6,12)
f7r2 <- f(0.5,0.6,7,12)
f8r2 <- f(0.5,0.6,8,12)
f9r2 <- f(0.5,0.6,9,12)
f10r2 <- f(0.5,0.6,10,12)
f11r2 <- f(0.5,0.6,11,12)
f12r2 <- f(0.5,0.6,12,12)

utilityr2 <- c(f0r2,f1r2,f2r2,f3r2,f4r2,f5r2,f6r2,f7r2,f8r2,f9r2,f10r2,f11r2,f12r2)
concentrationr2 <- c(0:12)

#print(utilityr2)
plot(concentrationr2,utilityr2)

```{r utzero, echo=FALSE, fig.cap="Results with desired fraction p = 0 in Moore neighborhood 8 patches, M=0.6 and Z=1"}

f0t8 <- f(0,0.6,0,8)
f1t8 <- f(0,0.6,1,8)
f2t8 <- f(0,0.6,2,8)
f3t8 <- f(0,0.6,3,8)
f4t8 <- f(0,0.6,4,8)
f5t8 <- f(0,0.6,5,8)
f6t8 <- f(0,0.6,6,8)
f7t8 <- f(0,0.6,7,8)
f8t8 <- f(0,0.6,8,8)

utilityt8 <- c(f0t8,f1t8,f2t8,f3t8,f4t8,f5t8,f6t8,f7t8,f8t8)
concentrationt8 <- c(0:8)

# print(utilityt8)
plot(concentrationt8,utilityt8)

>>>>

# v_w <- 1 - e_w

f_eth <- function(i_e,M,x,n,S){
  if (x > n){
    U <- NA}else{
  if (x < round(n*i_e,digits = 2)){
   U <- (x / round((n*i_e),digits = 2)) * S
    }else if (x > round((n*i_e),digits = 2)){
      U <- M + ((1- round((x/n),digits = 2))*(1-M))/(1-i_e)
    }else{
        U <- 1}
  round(U,digits = 2)
    }
}

f_val <- function(e_w,ew_ng,M,i_v,S){
  if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
    U <- 1
    }else{
      U <- (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S
    }
  round(U,digits = 2)
}

prob <- function(e_w,v_w,d_u_e,d_u_v){1 / (1 + exp(-e_w*(d_u_e)) + exp(-v_w*(d_u_v)))}

@@

@@

```{r ethnic_utility, moore neighborhood}

#i_e = 0.5
M = 0
S = 1
n = 8

for (i_e in seq (0.0,1.0, by = 0.1)){

f0m <- f_eth(i_e,M,0,n,S)
f1m <- f_eth(i_e,M,1,n,S)
f2m <- f_eth(i_e,M,2,n,S)
f3m <- f_eth(i_e,M,3,n,S)
f4m <- f_eth(i_e,M,4,n,S)
f5m <- f_eth(i_e,M,5,n,S)
f6m <- f_eth(i_e,M,6,n,S)
f7m <- f_eth(i_e,M,7,n,S)
f8m <- f_eth(i_e,M,8,n,S)

num_sim_col <- seq(0, 8, by = 1)
Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)

plot(num_sim_col,Utility_E, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)

report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_E)

print(report_E)

}
```

@@

i_v <- 0
S  <- 1
M <- 0

@@

for (e_w in seq (0.0,1.0, by = 0.1)){

fv0d2 <- f_val(e_w,0,M,i_v,S)
fv1d2 <- f_val(e_w,0.1,M,i_v,S)
fv2d2 <- f_val(e_w,0.2,M,i_v,S)
fv3d2 <- f_val(e_w,0.3,M,i_v,S)
fv4d2 <- f_val(e_w,0.4,M,i_v,S)
fv5d2 <- f_val(e_w,0.5,M,i_v,S)
fv6d2 <- f_val(e_w,0.6,M,i_v,S)
fv7d2 <- f_val(e_w,0.7,M,i_v,S)
fv8d2 <- f_val(e_w,0.8,M,i_v,S)
fv9d2 <- f_val(e_w,0.9,M,i_v,S)
fv10d2 <- f_val(e_w,1.0,M,i_v,S)

value_mean_neighborhood <- seq(0.0, 1.0, by = 0.1)
Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
name <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)

@@

report_v <- paste0(name,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)

print(report_v)

@@

@@

# prob <- function(e_w,s,t,v_w,p,q){1 / (1 + exp(-e_w*(d_u_e)) + exp(-v_w*(d_u_v)))}

# Make: foreach d_u_e [0-1], v_u_e spans within each [0-1]

prob1 <- prob(100,300,100,1,100,100)

plot(prob1)
```

@@
